Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-15 paper/main.tex
some cleaning of supplementals

\todo[inline]{SE: use different colormap for overlap of contrasts' clusters}

@@

\todo[inline]{SE: wie unterscheiden sich die Kontraste?}
\todo[inline]{Wo sind welche Kontraste (z.B. im Ergebnis) von anderen abgewichen?}

% PPA AV
Regarding contrasts of the AV stimulus (see Table \ref{tab:av-contrasts}), all
five AV contrasts show significant bilateral clusters in the PPA but also
extending into more posterior brain regions.
% PPA AD
Regarding contrasts of the AD stimulus (see Table \ref{tab:ao-contrasts}), six
of overall eight contrasts show significant bilateral clusters in the anterior
part of the group PPA overlap.
% results indicate robustness
Thus, the results of the additional contrasts indicate that our findings are
robust and do not depend on the design of one specific contrasts.
% but
Nevertheless, results are sensitive to the contrasted categories and the amount
of available data.
% example
For example, contrast 8 of the AD stimulus (\texttt{se\_new} > \texttt{se\_old})
that used the most heterogeneous categories comprising the least amount of
events yielded neither a significant cluster in the right-hemispheric nor
left-hemispheric PPA.
% concluding statement
Hence, investigators that use model-driven analyses have to consider how many
events a naturalistic stimulus may provide and how homogeneous the events to be
averaged might be.

% intro
Apart from the PPA, we find significantly increased activity in the dorsal
precuneus and posterior cingulate region (e.g. retrosplenial cortex; RSC) and
lateral occipital cortex (LOC) across contrasts of both naturalistic stimuli.
% RSC intro
Like the PPA, the RSC (AV stimulus: significant clusters in 3 of 5 contrasts; AD
stimulus: 7 of 8 contrasts) and LOC (AV stimulus: 4 of 5 contrasts; AD stimulus:
unilateral in 2, bilateral in 4 of 8 contrasts) are known to be scene-selective
regions (see \citep{chrastil2018heterogeneity, bettencourt2013role} for
reviews).\todo{same part as in the main text but with number of contrasts}

% some backup text for RSC & LOC
\begin{comment}
% RSC
RSC is located in the retrosplenial cortex, and posterior cingulate region (BA
23 and 31) [51–56], near to the point where the calcarine sulcus joins the
parietal-occipital sulcus \citep{epstein2008parahippocampal}.
%
RSC location functionally defined. In context of scene perception, the RSC is
not necessarily spatially congruent with the anatomically defined retrosplenial
cortex [26] (BA 29 and 30) \citep{epstein2008parahippocampal} but functionally
defined as the posterior medial region that exhibits increased hemodynamic
activity to visual scenes and during mental imagination trough familiar
environments [8] \citep{epstein2008parahippocampal}.

\begin{itemize}
    \item \citep{chrastil2018heterogeneity}
    \item \citep{vann2009what}
    \item \citep{silson2019posterior}
    \item \citep{baldassano2016two}:
    \item RSC appears to be most directly involved in orienting the viewer to
    the structure of the environment (both within and beyond the borders of the
presented image) for the purpose of navigational planning; it encodes both
absolute location and facing direction [Vass and Epstein, 2013; Epstein and
Vass, 2014; Marchette et al., 2014], integrates across views presented in a
panoramic sequence [Park and Chun, 2009], and shows strong familiarity effects
[Epstein et al., 2007a,b].
\end{itemize}

% LOC
\begin{itemize}
\item Bettencourt (2013). The Role of Transverse Occipital Sulcus in Scene
    Perception
\item Dilks, Kanwisher (2013). The Occipital Place Area Is Causally and
    Selectively Involved in Scene Perception
\item Nasr (2011). Scene-selective cortical regions in human and nonhuman
    primates
\item Dilks (2011). Mirror-image sensitivity and invariance in object \& scene
    processing
\item MacEvoy and Epstein (2007). Position selectivity in scene- and
    object-responsive
\item Grill-Spector (2003). The neural basis of object perception
\item Hasson (2003). Large-scale mirror-symmetry organization
\item Nakamura (2000). Functional delineation of the human occipito-temporal
    areas
\item \citep{baldassano2016two} regarding functional difference pPPA vs. OPA:
    The functional distinction is unclear.
    Previous work has speculated about the purpose of the apparent ventral and
    dorsal ``duplication'' of regions sensitive to large landmarks, proposing
    that it may be related to different output goals (e.g., action planning in
    OPA, object recognition in pPPA)[Konkle and Caramazza, 2013], or to
    different input connections (e.g., lower visual field processing in OPA,
    upper visual field processing in pPPA)[Kravitz et al., 2013; Silson et al.,
    2015].
    OPA and pPPA may also use information from different visual
    eccentricities: OPA processing less peripheral, relatively high-resolution
    environmental features. pPPA processing more peripheral, large-scale
    geometry, and context [Baldassano et al., 2016a]
\end{itemize}

\end{comment}

% ``confounding'' clusters
Despite performing a whole brain analysis, we do not find many [random] clusters
in single contrasts or even systematically across contrasts that hamper the
interpretation of results.
% AV: null results regarding attention and eye movements
For example in the AV results, we do not find significant clusters that could be
attributed to cognitive processes like attention or eye movements.
% AD: auditory cortices
Nevertheless, contrasts of the AD stimulus that compare (among others) verbal
hints of the change of a setting (\texttt{se\_new} or \texttt{se\_old}) to all
non-spatial categories (cf. contrasts 2, 3, 6, 7) show significant clusters in
(primary and secondary) auditory cortices.
% averaging vs. nuisance regressors
This suggests that variance correlating with lower level auditory processes was
not averaged out across trials and nuisance regressors did not capture enough
variance.
% possible reason
Significant clusters in auditory cortices could be correlating with a possible
change of the soundscape when the narrator of the audio-description (or a cut in
the movie) switches to a another setting.
% concluding statement
Thus, investigators that use model-driven methods to investigate brain functions
using naturalistic stimuli should (extensively) annotate the stimulus material
and test for correlations among variables.

@@

% intro
For the purpose of negative control, we implemented five contrasts for every
stimulus.

% ---------- AV control contrasts ----------
% 6 nothing
% 7 nothing
% 8 nothing
% 9 nothing
%10 se_new > se_old (nouns but in AV stimulus):
% LOC (l/r) right PPA, bilateral sup. lat. occ. c., sup. parietal lobe (right)

@@

% AV: no_cut > x
In the analysis of the AV data, none of the four contrasts that compared the
\texttt{no\_cut} category to a movie cut category (see Table
\ref{tab:av-contrasts}) yielded significant clusters.
% AV using nouns
The contrast that used the narrator's nouns but in the AV stimulus
(\texttt{se\_new} > \texttt{se\_old}) yielded a significant cluster in the right
PPA and bilateral clusters in the superior lateral occipital cortices (the right
hemispheric cluster extending into the superior parietal cortex).\todo{cuts
correlate with the nouns}

% AD stimulus
In the analysis of the AD data, we created control contrasts based on events of
the annotated movie cuts (cf. Table \ref{tab:ao-contrasts})
% contrast 9
Contrast 9 (vse\_new > pe\_old) revealed one significant cluster in the left
inferior prefrontal cortex (pars triangularis) and right ventral
precuneus/posterior cingulate gyrus.
% contrast 12
Contrast 12 (\texttt{vse\_new} > \texttt{vse\_old}, \texttt{vpe\_old}) revealed
one cluster in the right posterior hippocampus.\todo{odd imo}

@@

The four control contrasts of the AV stimulus that compared the
\texttt{no\_cuts} to categories of movie cuts all lead to null results.

% AD anno in AV data
The AV contrast using nouns (\texttt{se\_new} > \texttt{se\_old}): PPA
(unilateral), LOC (bilateral); These noun categories show highest correlation
among nouns with their cut counterpart \texttt{se\_new} (nouns) is r$\approx$0.3
correlated with \texttt{vse\_new} (cuts); \texttt{se\_old} (nouns) is
r$\approx$0.4 correlated with \texttt){vse\_old}.

>>>>

\todo[inline]{SE: use different colormap for overlap of contrasts' clusters}
\todo[inline]{SE: wie unterscheiden sich die Kontraste?}
\todo[inline]{Wo sind welche Kontraste (z.B. im Ergebnis) von anderen abgewichen?}

@@

% Discussion
The results across the contrasts of the AV and AD stimulus indicate that our
findings regarding the PPA but also RSC and LOC are robust and do not depend on
the design of one specific contrasts.
% but
Nevertheless, results are sensitive to the contrasted categories and the amount
of available data.
% example
For example, contrast 8 of the AD stimulus (\texttt{se\_new} > \texttt{se\_old})
that used the most heterogeneous categories comprising the least amount of
events yielded neither a significant cluster in the right-hemispheric nor
left-hemispheric PPA.
% concluding statement
Hence, investigators that use model-driven analyses have to consider how many
events a naturalistic stimulus may provide and how homogeneous the events to be
averaged might be.

% ``confounding'' clusters
Despite performing a whole brain analysis, we do not find [many] clusters
in a single contrasts or systematically across contrasts that are scattered
across the brain and hamper the interpretation of results.
% AV: null results regarding attention and eye movements
For example in the AV results, we do not find significant clusters that could be
attributed to cognitive processes like attention or eye movements.
% AD: auditory cortices
Nevertheless, contrasts of the AD stimulus that compare (among others) verbal
hints of the change of a setting (\texttt{se\_new} or \texttt{se\_old}) to all
non-spatial categories (cf. contrasts 2, 3, 6, 7) show significant clusters in
(primary and secondary) auditory cortices.
% averaging vs. nuisance regressors
This suggests that variance correlating with lower level auditory processes was
not averaged out across trials and nuisance regressors did not capture enough
variance.
% possible reason
Significant clusters in auditory cortices could be correlating with a possible
change of the soundscape when the narrator of the audio-description (or a cut in
the movie) switches to a another setting.
% concluding statement
Thus, investigators that use model-driven methods to investigate brain functions
using naturalistic stimuli should (extensively) annotate the stimulus material
and test for correlations among variables.

\todo[inline]{random [?] prefrontal cluster in 2-3 AO contrasts; at the moment
no idea what the correlating process could be; be aware of reverse inferences}

@@

\todo[inline]{discuss results in light of ``negative control'' (-> definition \&
purpose}

% ---------- AV control contrasts ----------
% 6 nothing 7 nothing 8 nothing 9 nothing
%10 se_new > se_old (nouns but in AV stimulus): LOC (l/r) right PPA, bilateral
%sup. lat. occ. c., sup. parietal lobe (right)

@@

% intro
For the purpose of negative control, we implemented five contrasts for every
stimulus.
% AV: no_cut > x
In the analysis of the AV data, none of the four contrasts that compared the
\texttt{no\_cut} category to a movie cut category (see Table
\ref{tab:av-contrasts}) yielded significant clusters.
% AV using nouns
The contrast that used the narrator's nouns but in the AV stimulus
(\texttt{se\_new} > \texttt{se\_old}) yielded a significant cluster in the right
PPA and bilateral clusters in the superior lateral occipital cortices (the right
hemispheric cluster extending into the superior parietal cortex).
% AD stimulus
In the analysis of the AD data, we created control contrasts based on events of
the annotated movie cuts (cf. Table \ref{tab:ao-contrasts})
% contrast 9
Contrast 9 (vse\_new > pe\_old) revealed one significant cluster in the left
inferior prefrontal cortex (pars triangularis) and right ventral
precuneus/posterior cingulate gyrus.
% contrast 12
Contrast 12 (\texttt{vse\_new} > \texttt{vse\_old}, \texttt{vpe\_old}) revealed
one cluster in the right posterior hippocampus.\todo{odd imo}

@@

The four control contrasts of the AV stimulus that compared the
\texttt{no\_cuts} to categories of movie cuts all lead to null results.
% AD anno in AV data
The AV contrast using nouns (\texttt{se\_new} > \texttt{se\_old}): PPA
(unilateral), LOC (bilateral); These noun categories show highest correlation
among nouns with their cut counterpart \texttt{se\_new} (nouns) is r$\approx$0.3
correlated with \texttt{vse\_new} (cuts); \texttt{se\_old} (nouns) is
r$\approx$0.4 correlated with \texttt){vse\_old}.
